A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-11-15 writeup/version1/paper.tex
rewrite

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[fit]{truncate}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{multirow}
\usepackage{dblfloatfix}
\usepackage{float}
\usepackage{subfigure}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{5cm}    % Expanding the titlebox

@@

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{final-figures/turkermap}
\caption{The number of workers per country.  This map was generated based on geolocating the IP address of  5,277 workers in our study.  The size of the circles represents the number of workers from each country.  The two largest are India (2,017 workers) and the United States (904).  To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
\begin{table}
\footnotesize
\begin{tabular}{lrlrlr}\hline\hline
%Language&\# Turkers\\
\hline
English&592&	French&63&	Vietnamese&34\\
Tamil&253&	Polish&61&	Macedonian&31\\
Malayalam&219&	Urdu&56&	Cebuano&29\\
Hindi&149&	Tagalog&54&	Swedish&26\\
Spanish&131&	Marathi&48&	Bulgarian&25\\
Telugu&87&	Russian&44&	Hungarian&23\\
Chinese&86&	Italian&43&	Swahili&23\\
Romanian&85&	Bengali&41&	Thai&22\\
Portuguese&82&	Gujarati&39&	Catalan&22\\
Arabic&74&	Hebrew&38&	Lithuanian&21\\
Kannada&72&	Dutch&37&	Punjabi&21\\
German&66&	Turkish&35&	Others &$\leq$20\\
\hline\hline
\end{tabular}
\normalsize
\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 languages with $\leq$20 speakers. 
We omit 1,797 Turkers who did not report their native language, 243 who reported 2 native languages, and 83 with $\geq$3 native languages.}\label{lang-pie}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\begin{center}
\includegraphics[width=0.8\linewidth]{final-figures/quality-bar}
\caption{Translation quality for languages with at least 50 Turkers.  The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.}
\label{hitlangqual} 
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
\begin{figure}[h]
\includegraphics[height=\linewidth,angle=270]{final-figures/completetime}
\caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
\label{completion-time}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\begin{table*}
\scriptsize
\begin{center}
\begin{tabular}{lllll}
\hline\hline
&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
&In region&Out of region&of Turkers in region&of Turkers out of region\\
\hline\hline
Hindi&\textbf{0.35} (299)&0.34 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
Tamil&\textbf{0.37} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
Malayalam&0.48 (235) &\textbf{0.58} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
Spanish&\textbf{0.72} (205)&0.61 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
French&0.65 (183) &\textbf{0.86} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
German&\textbf{0.83} (99)&0.65 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
Italian&\textbf{0.78} (98)&0.71 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
Chinese&\textbf{0.24} (121)&0.16 (19)&US (79) Singapore (15) China (14) &Hong Kong (6) Australia (3) Germany (2) \\
Malay&0.76 (15) &\textbf{0.83} (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
Irish&\textbf{0.68} (58)&0.64 (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
Czech&\textbf{0.71} (52)&0.63 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
Turkish&0.72 (83) &\textbf{0.73} (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
Amharic&\textbf{0.18} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
Swedish&\textbf{0.66} (58)&0.61 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
Portuguese&\textbf{0.77} (107)&0.74 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
Arabic&0.22 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
Kannada&\textbf{0.24} (106)&0.00 (1)&India (106) US (1) &France (1) Germany (1) \\
Russian&\textbf{0.09} (72)&0.06 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
Afrikaans&\textbf{0.74} (4)&0.73 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
Sindhi&\textbf{0.15} (93)&0.02 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
\hline\hline
\end{tabular}
\normalsize
\end{center}
\caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.} \label{region-summary}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1\linewidth]{final-figures/google-match}
\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.42}
\label{googlematch} 
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
\begin{figure*}[h]
\begin{center}
\includegraphics[width=0.8\linewidth]{final-figures/quality-scatter_joined}
\end{center}

\caption{Estimated quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country. Quality is calculated as the average number of control words which were correct translations of the source word, where ”correct” means that the provided translation was judged to be synonymous with the known translation by workers in a second-pass HIT. Figure represents data from approx. 295,000 assignments for which geolocation was known.}
\label{quality-scatter}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Figure \ref{quality-scatter} shows the number of assignments completed per country and per-country quality estimates for 4 scenerios: (a) overall, (b) for assignments completed in region, (c) for assignments completed out of region, and (d) for out of region assignments which contained low overlap with GoogleTranslate.

@@

@@

We used GoogleTranslate to translate all 10,000 words for 50 foreign languages that GoogleTranslate covers. We measured the percent of translations received that exactly matched the translation returned from GoogleTranslate. Results are show in Figure \ref{googlematch}. 
Assignments averaged around 42\% overlap with GoogleTranslate.  Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphabet) have lower overlap with Google,  suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet. 
% suggesting that it is easier for Turkers to use MT for Latin alphabet languages.

%We translated: af ar az bg ca cs cy da de el eo es eu fa fi fr gl gu he hr hu hy id is it ja kn ko lt lv ms nl pl pt ro ru sk sl sq sr sv sw ta te th tr uk ur vi zh

% Google supports:
%Afrikaans
%Albanian
%Arabic
%Belarusian
%Bulgarian
%Catalan
%Chinese
%Chinese
%Croatian
%Czech
%Danish
%Dutch
%English
%Estonian
%Esperanto
%Filipino
%Finnish
%French
%Galician
%German
%Greek
%Hebrew
%Hindi
%Hungarian
%Icelandic
%Indonesian
%Irish
%Italian
%Japanese
%Korean
%Latvian
%Lithuanian
%Macedonian
%Malay
%Maltese
%Norwegian
%Persian
%Polish
%Portuguese
%Romanian
%Russian
%Serbian
%Slovak
%Slovenian
%Spanish
%Swahili
%Swedish
%Thai
%Turkish
%Ukrainian
%Vietnamese
%Welsh
%Yiddish
%Armenian
%Azerbaijani
%Basque
%Georgian
%Gujarati
%Haitian Creole
%Kannada
%Latin
%Lao
%Tamil
%Telugu
%Urdu

@@

>>>>

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[fit]{truncate}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{multirow}
\usepackage{dblfloatfix}
\usepackage{float}
\usepackage{subfloat}
\usepackage{subcaption}

\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{5cm}    % Expanding the titlebox

@@

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{../version1-figures/map.png}
\caption{The number of workers per country.  This map was generated based on geolocating the IP address of  5,277 workers in our study.  The size of the circles represents the number of workers from each country.  The two largest are India (2,017 workers) and the United States (904).  To calibrate the sizes: the Philippines has 147 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% NAT LANG PIE TABLE %%%%%%%%%%%
\begin{table}
\footnotesize
\begin{tabular}{lrlrlr}\hline\hline
%Language&\# Turkers\\
\hline
English & 689 & Tamil & 253 & Malayalam & 219 \\
Hindi & 149 & Spanish & 131 & Telugu & 87 \\
Chinese & 86 & Romanian & 85 & Portuguese & 82 \\
Arabic & 74 & Kannada & 72 & German & 66 \\
French & 63 & Polish & 61 & Urdu & 56 \\
Tagalog & 54 & Marathi & 48 & Russian & 44 \\
Italian & 43 & Bengali & 41 & Gujarati & 39 \\
Hebrew & 38 & Dutch & 37 & Turkish & 35 \\
Vietnamese & 34 & Macedonian & 31 & Cebuano & 29 \\
Swedish & 26 & Bulgarian & 25 & Swahili & 23 \\
Hungarian & 23 & Catalan & 22 & Thai & 22 \\
Lithuanian & 21 & Punjabi & 21 & Others & $\leq$ 20 \\
\hline\hline
\end{tabular}
\normalsize
\caption{Self-reported native language of 3,154 bilingual Turkers. Not shown are 54 languages with $\leq$20 speakers. 
We omit 1,797 Turkers who did not report their native language, 243 who reported 2 native languages, and 83 with $\geq$3 native languages.}\label{lang-pie}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\begin{center}
\includegraphics[width=\linewidth]{../version1-figures/quality_bar.png}
\caption{Translation quality for languages with at least 50 Turkers.  The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms.}
\label{hitlangqual} 
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
\begin{figure}[h]
\includegraphics[height=\linewidth,angle=270]{../final-figures/completetime}
\caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
\label{completion-time}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\begin{table*}
\scriptsize
\begin{center}
\begin{tabular}{lllll}
\hline\hline
&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
&In region&Out of region&of Turkers in region&of Turkers out of region\\
\hline\hline
Hindi & 0.636 (291) & \textbf{0.715} (6) & India (279) Uae (5) Uk (3)  & Russia (1) Oman (1) Denmark (1) \\
Tamil & \textbf{0.652} (267) * & 0.250 (2) & India (260) Unitedstates (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
Malayalam & 0.763 (233) & \textbf{0.827} (2) & India (222) Uae (6) Unitedstates (3)  & Saudiarabia (1) Maldives (1) \\
Spanish & \textbf{0.794} (152) & 0.788 (12) & Unitedstates (98) Mexico (16) Spain (12)  & India (10) Newzealand (1) Macedonia (1)  \\
French & 0.744 (146) & \textbf{0.816} (11) & India (50) Unitedstates (37) France (22)  & Greece (2) Netherlands (1) Japan (1) \\
Chinese & \textbf{0.597} (115) & 0.597 (19) & Unitedstates (74) Singapore (13) China (9)  & Hongkong (6) Australia (3) Germany (2)  \\
German & \textbf{0.818} (81) & 0.769 (37) & Germany (45) Unitedstates (22) Austria (6)  & India (31) Netherlands (1) Greece (1)  \\
Amharic & \textbf{0.136} (16) * & 0.009 (99) & Unitedstates (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
Kannada & 0.704 (105) & NA (0) & India (105)  & \\
Sindhi & \textbf{0.190} (96) & 0.062 (9) & India (58) Pakistan (37) Unitedstates (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
Italian & \textbf{0.857} (72) & 0.775 (32) & Italy (37) Unitedstates (19) Romania (6)  & India (25) Ireland (2) Spain (2)  \\
Arabic & \textbf{0.732} (58) * & 0.607 (44) & Egypt (19) Jordan (16) Morocco (8)  & Unitedstates (19) India (11) Canada (3)  \\
Telugu & \textbf{0.796} (100) & 0.500 (1) & India (96) Unitedstates (3) Uae (1)  & Saudiarabia (1)  \\
Turkish & 0.749 (69) & \textbf{0.779} (23) & Turkey (37) Unitedstates (16) Macedonia (5)  & India (16) Pakistan (4) Tunisia (1) \\
Breton & 0.167 (3) & \textbf{0.178} (89) & Unitedstates (3)  & India (83) Macedonia (2) China (1) \\
Russian & \textbf{0.148} (64) & 0.120 (24) & Unitedstates (33) Moldova (7) Russia (6)  & India (12) Macedonia (4) Uk (3)  \\
Pashto & \textbf{0.495} (20) * & 0.051 (68) & Pakistan (20)  & India (59) Georgia (2) Macedonia (2)  \\
Irish & \textbf{0.740} (51) & 0.717 (36) & Unitedstates (36) Ireland (13) Uk (2)  & India (28) Romania (3) Pakistan (2)  \\
Tagalog & \textbf{0.849} (76) & 0.825 (9) & Philippines (60) Unitedstates (14) Canada (1)  & Taiwan (2) India (2) Bangladesh (1)  \\
Marathi & 0.654 (82) & \textbf{0.833} (3) & India (80) Mauritius (1) Unitedstates (1)  & Uae (1) Oman (1) Ukraine (1) \\

\hline\hline
\end{tabular}
\normalsize
\end{center}
\caption{Translation quality when partitioning the translations into two groups, one contains translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other contains translations from Turkers outside those regions.} \label{region-summary}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure}[h]
\begin{center}
\includegraphics[width=1\linewidth]{../version1-figures/google_bar.png}
\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.37.}
\label{googlematch} 
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% QUALITY / NUM ASSIGN SCATTER %%%%%%%%%%%
%\begin{figure}
%\begin{center}
%\includegraphics[width=0.78\linewidth]{../final-figures/quality-scatter_joined-1column}
%\end{center}

%\caption{Estimated quality of translations by country. Each circle is a country, sized proportional to the number of active Turkers from that country. }
%\label{quality-scatter}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Figure \ref{quality-scatter} shows the number of assignments completed per country and per-country quality estimates for 4 scenerios: (a) overall, (b) for assignments completed in region, (c) for assignments completed out of region, and (d) for out of region assignments which contained low overlap with GoogleTranslate.

@@

\begin{figure}
\centering
\begin{subfigure}[b]{1\linewidth}
\includegraphics[width=\textwidth]{../version1-figures/turker-googmatch-distribution.png}
\caption{Individual turker overlap with google translate. We believe the inflection point at ~60\% overlap with Google suggests a reasonable cutoff by which to filter workers. Workers with \textgreater 60\% overlap can be reasonably considered to be cheating and can be removed.}                
\label{dist}
\end{subfigure}
\begin{subfigure}[b]{1\linewidth}
\includegraphics[width=\textwidth]{../version1-figures/google-cdf-googlangs.png}
\caption{Cumulative distribution of overlap with Google translate for workers and translations. We see that eliminating all workers with \textgreater 60\% overlap with google translate still preserves \textgreater 80\% of workers and \textgreater 70\% of translations.}
\label{cdf}
\end{subfigure}
\caption{}\label{cheaters}
\end{figure}

@@

We used GoogleTranslate to translate all 10,000 words for 50 foreign languages that GoogleTranslate covers. We measured the percent of translations received that exactly matched the translation returned from GoogleTranslate. Results are show in Figure \ref{googlematch}. 
Assignments averaged around 42\% overlap with GoogleTranslate.  Languages with non-Latin scripts (such as the Arabic script, Chinese characters or the Telugu alphabet) have lower overlap with Google,  suggesting that it is easier for Turkers to cheat for languages written in the Latin alphabet.

@@

\section{Application to SMT}
With the dictionaries in hand, we moved on to translate the entire
Wikipedia documents.  Each human intelligence task (HIT) posted on
MTurk contained ten sequential source-language sentences from a
document, and asked the worker to enter a free-form translation for
each.  We collected four translations from different translators for
each source sentence.  To discourage cheating through
cutting-and-pasting into automatic translation systems, sentences were
presented as images.  Workers were paid \$0.70 per HIT.  We then
manually determined whether to accept or reject a worker's HITs based
on a review of each worker's submissions, which included a comparison
of the translations to a monotonic gloss (produced with the
dictionary), the percentage of empty translations, the amount of time
the worker took to complete the HIT, geographic
location (self-reported and geolocated by way of the worker's
IP address), and by comparing different translations of the same
source segments against one another.

We obtained translations of the
source-language documents in a relatively short amount of time. Malayalam provided the highest throughput,
generating half a million words in just under a week.  For comparison,
the Europarl corpus \cite{koehn2005europarl} has about 50 million
words of English for each of the Spanish and French parallel corpora.

The tradeoff for low-cost translations is increased variance in
translation quality when compared to the more consistently-good
professional translations.  Figure~\ref{figure:variance} contains some
hand-picked examples of the sorts of translations we obtained.  Later,
in the Experiments section (\S\ref{section:experiments}), we will
investigate the effects this variance in translation quality has on
the quality of the models that can be constructed.  For now, the
variance motivated the collection of an additional dataset, described
in the next section.

A prevailing issue with translations collected on MTurk is the
prevalence of low-quality translations.  Quality suffers for a variety
of reasons: Turkers lack formal training, often translate into a
nonnative tongue, may give insufficient attention to the task, and
likely desire to maximize their throughput (and thus their wage).
Unlike \newcite{zaidan2011crowdsourcing}, who embed controls
containing source language sentences with known professional
translations, we had no professionally translated data.  Therefore, we
could not measure the BLEU score of the Turkers.

Motivated by desire to have some measure of the relative quality and variance of the translations,
we designed another task in which we presented an independent set of Turkers with an original
sentence and its four translations, and asked them to vote on which was best.\footnote{We did not
  collect votes for Malayalam.}  Five independent workers voted on the translations of each source
sentence.  Tallying the resulting votes, we found that roughly 65\% of the sentences had five votes
cast on just one or two of the translations, and about 95\% of the sentences had all the votes cast
on one, two, or three sentences.  This suggests both (1) that there was a difference in the quality
of the translations, and (2) the voters were able to discern these differences, and took their task
seriously enough to report them.

\begin{table}[t]
\centering
\begin{tabular}{l|rr}
  language  & SAMT &  Google \\
  \hline\hline
  Bengali    & 13.53  &  20.01 \\
  Hindi      & 17.29  & 25.21 \\  
  Malayalam    & 14.28  & - \\      
  Tamil      &  9.85  &  13.51 \\  
  Telugu     & 12.61  & 16.03  \\  
  Urdu        & 20.99  & 23.09 \\   
\end{tabular}
\caption{BLEU scores translating into English (four references).  BLEU
scores are the mean of three MERT runs.}
\label{table:bleu}
\end{table}

\begin{figure*}[t]
  \centering
  \includegraphics[width=\textwidth]{../version1-figures/tamil.png}
  \begin{tabular}{l}
    \hline
    In March 15,2007 Wiki got a place in Oxford English dictionary. \\
    On March 15, 2007 wiki was included in the Oxford English
    dictionary. (5) \\
    ON MARCH 15, 2007, WIKI FOUND A PLACE IN THE OXFORD ENGLISH
    DICTIONARY \\
    March 15, 2007 oxford english index of wiki's place. \\ \\

  \end{tabular}
  \caption{An example of the variance in translation quality for the
    human translations of a Tamil sentence; the formatting of the
    translations has been preserved exactly.  The parenthesized number
    indicates the number of votes received in the voting task
    (\S\ref{section:votes}).}
  \label{figure:variance}
\end{figure*}
